Dynamics of innovation in stigmergic collectives

### 2023-04-27 LaTeX/draft.tex
ModeAddns

%\pacs{Valid PACS appear here}
\maketitle
\section{Problem setting}
Let us consider a trail of pheromone $\x^*(s)$ representing the position in 2-D coordinates and parameterized by the
arc-length $s$. The concentration of pheromone is considered continuous along this curve and is given by $c(\x) = c_o \delta(\x-\x^*(s))$.
This field is of course steady and its dynamics will be considered later in the article. The state of the agent/ant in
the environment is is represented by its position $\r^t=\{ r_x^t, r_y^t \}$ and the action it can take is to choose the
direction of motion i.e., its orientation $\ph^t = \{\cos(\theta^t), \sin(\theta^t)\}$, where $[\bullet]^t$ denotes the
value of the variable at time-instant $t$. The agent can choose the action based on the measurements at each instant of time.
In this article we are interested in understanding how and when an agent can innovate from its innate behavior to follow
pheromone trail to explore the environment and find novel solutions to the navigation problem.

@@

>>>>

%\pacs{Valid PACS appear here}
\maketitle
\section{Problem setting}
Let us consider a trail of pheromone $\x^*(s)$ representing the position in 2-D coordinates and parameterized by the
arc-length $s$. The concentration of pheromone is considered continuous along this curve and is given by $c(\x) = c_o \delta(\x-\x^*(s))$.
This field is of course steady and its dynamics will be considered later in the article. The state of the agent/ant in
the environment is is represented by its position $\r^t=\{ r_x^t, r_y^t \}$ and the action it can take is to choose the
direction of motion i.e., its orientation $\ph^t = \{\cos(\theta^t), \sin(\theta^t)\}$, where $[\bullet]^t$ denotes the
value of the variable at time-instant $t$. The agent can choose the action based on the measurements at each instant of time.
In this article we are interested in understanding the dynamics of agents that need to innovate in order to find new
trails over which the collective travels. In order to understand the dynamics, we assume that the agent has already
traveled along the trajectory $\x^*(s)$ once before.
In this article we are interested in understanding how and when an agent can innovate from its innate behavior to follow
pheromone trail to explore the environment and find novel solutions to the navigation problem.

@@

\subsection*{Search strategy post bifurcation}
After the agent leaves the trail trajectory at $\r(s_c)$, the agent needs to reach the target A.
